Extending K-Means Clustering with Ptolemy’s Inequality

### 2024-10-02 content/4_contribution.tex
fixing bugs

%\newcommand{\coo}{c^{\diamond}}
\newcommand{\prev}{\diamond}

@@

  The process is similar for Eq.~\ref{eq:pto_lower}; as the signs on the right hand side are not equal in this case, there are two distinct ways to substitute Ptolemy's inequality.
  This gives rise to the two inequalities shown inside the maximum function.
  Analogous to the previous term, the right-hand side of Eq.~\ref{eq:pto_lower} can only be made smaller by inserting lower bounds in the minuend or upper bounds in the subtrahend.
  Thus, $d(x_i, c_j') & \geq l_{i,j}'$ also holds.
\end{proof}

>>>>

\newcommand{\prev}{\diamond}

@@

	The process is similar for Eq.~\ref{eq:pto_lower}; as the signs on the right-hand side are not equal in this case, there are two distinct ways to substitute into Ptolemy's inequality.
	This gives rise to the two inequalities, of which the maximum is the stronger bound.
	Analogous to $u'_i$, the right-hand side of Eq.~\ref{eq:pto_lower} can only be made smaller by inserting lower bounds of the distance $l_{i,j},l_{i,j}^\prev$ in the minuend or upper bounds $u_i, u^\prev_i$ in the subtrahend.
	Thus, $d(x_i, c_j') \geq l_{i,j}'$ also holds.
\end{proof}
